StackTokens: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-01 fully-abstract-comp/popl2019/paper.tex
Propose a name for our calling convention: StackTokens.

%% Title information
\title{Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities}
% \titlenote{with title note}
% \subtitle{Fully abstract overlay semantics}
% \subtitlenote{with subtitle note}

@@

\begin{abstract}
We propose and study a new calling convention that provably enforces well-bracketed control flow and local state encapsulation on a capability machine.
The calling convention is based on linear capabilities, a type of capabilities that are prevented by the hardware from being duplicated.
In addition to designing and formalising this new calling convention, we also contribute a new way to formalise and prove that it effectively enforces well-bracketed control flow and local state encapsulation, using what we call a fully abstract overlay semantics.
\end{abstract}

@@

In this work, we propose and study another way to enforce well-bracketed control flow and local state encapsulation with a single shared stack.
Instead of CHERI's local capabilities, we build on \emph{linear} capabilities; a new form of capabilities that has not been previously described in the published literature.\footnote{Although they are mentioned here and there by different people.} 
These capabilities are enforced by the hardware to be non-duplicable.
We propose to make stack and return pointers linear and require components to hand them out in cross-component invocations and to return them in returns.
The non-duplicability of linear capabilities, together with some security checks, then allows us to guarantee well-bracketed control flow and local stack frame encapsulation.

@@

>>>>

%% Title information
\title{StackTokens: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities}
% \titlenote{with title note}
% \subtitle{Fully abstract overlay semantics}
% \subtitlenote{with subtitle note}

@@

\begin{abstract}
We propose and study StackTokens: a new calling convention that provably enforces well-bracketed control flow and local state encapsulation on a capability machine.
The calling convention is based on linear capabilities, a type of capabilities that are prevented by the hardware from being duplicated.
In addition to designing and formalising this new calling convention, we also contribute a new way to formalise and prove that it effectively enforces well-bracketed control flow and local state encapsulation, using what we call a fully abstract overlay semantics.
\end{abstract}

@@

In this work, we propose and study StackTokens: an alternative calling convention that enforces well-bracketed control flow and local state encapsulation with a single shared stack.
Instead of CHERI's local capabilities, it builds on \emph{linear} capabilities; a new form of capabilities that has not been previously described in the published literature.\footnote{Although they are mentioned here and there by different people.} 
These capabilities are enforced by the hardware to be non-duplicable.
We propose to make stack and return pointers linear and require components to hand them out in cross-component invocations and to return them in returns.
The non-duplicability of linear capabilities, together with some security checks, then allows us to guarantee well-bracketed control flow and local stack frame encapsulation, without large overhead on boundary crossings and particularly no need for clearing large blocks of memory.

@@

\paragraph{Outline} Blabla
